### 2015-05-27 doc/manual/runs.tex
edited section 5.6 of user manual

By setting {\ttfamily RHSMode=3}, \sfincs~can be run in a mode
where it solves the same kinetic equation (prior to discretization) as {\ttfamily dkes}
and other monoenergetic codes.
When {\ttfamily RHSMode=3}, the values of {\ttfamily Zs}, {\ttfamily THats}, {\ttfamily nHats},
{\ttfamily mHats}, {\ttfamily nu\_n}, and {\ttfamily dPhiHatdXXX} are all ignored.
Instead, the collisionality is set by {\ttfamily nuPrime}, and the radial electric field is set
by {\ttfamily EStar}.  The first of these quantities is the dimensionless collisionality
\begin{equation}
\mbox{\ttfamily nuPrime} = \frac{(G+\iota I) \nu}{v B_0}
\end{equation}
where $G$ and $I$ are defined in (\ref{eq:covariant}), $\iota=1/q$ is the rotational transform,
$v$ is the speed at which the monoenergetic calculation is being performed, and $B_0$ is the (0,0) Fourier harmonic of $B$
with respect to the Boozer poloidal and toroidal angles.
\todo{How is $\nu$ defined here?}
The normalized radial electric field is
\begin{equation}
\mbox{\ttfamily EStar} = \frac{cG}{\iota v B_0} \frac{d\Phi}{d\psi}
\end{equation}
(Gaussian units).
When {\ttfamily RHSMode} == 1, {\ttfamily nuPrime} and {\ttfamily EStar} are ignored.
\todo{Should be change the behavior of RHSMode=2 so it uses nuPrime and EStar instead of nu\_n?}

>>>>

By setting {\ttfamily RHSMode=3}, \sfincs~can be run in a mode
where it solves the same kinetic equation (prior to discretization) as {\ttfamily dkes}
and other monoenergetic codes.
When {\ttfamily RHSMode=3}, the values of {\ttfamily Zs}, {\ttfamily THats}, {\ttfamily nHats},
{\ttfamily mHats}, {\ttfamily nu\_n}, and {\ttfamily dPhiHatdXXX} are all ignored.
Instead, the collisionality is set by {\ttfamily nuPrime}, and the radial electric field is set
by {\ttfamily EStar}.  The first of these quantities is the dimensionless collisionality
\begin{equation}
\mbox{\ttfamily nuPrime} = \frac{(G+\iota I) \nu}{v B_0}
\end{equation}
where $G$ and $I$ are defined in (\ref{eq:covariant}), $\iota=1/q$ is the rotational transform,
$v$ is the speed at which the monoenergetic calculation is being performed, and $B_0$ is the (0,0) Fourier harmonic of $B$
with respect to the Boozer poloidal and toroidal angles. The collision
frequency $\nu$ is here the value of $\nu_\mathrm{ii}$ one would have if
$v$ were the thermal speed. That is, in SI units,
\begin{equation}
  \nu=\frac{4}{3\sqrt{\pi}}\frac{n Z^4e^4\ln \Lambda}{4\pi\epsilon_0^2m^2v^3}.
\end{equation}
%
The normalized radial electric field is
\begin{equation}
\mbox{\ttfamily EStar} = \frac{cG}{\iota v B_0} \frac{d\Phi}{d\psi}
\end{equation}
(Gaussian units).
When {\ttfamily RHSMode} == 1, {\ttfamily nuPrime} and {\ttfamily EStar} are ignored.
\todo{Should be change the behavior of RHSMode=2 so it uses nuPrime and EStar instead of nu\_n?}

The two parameters {\ttfamily nuPrime} and {\ttfamily EStar} are
related to the corresponding DKES parameters {\ttfamily CMUL} and
{\ttfamily EFIELD} by
\begin{eqnarray}
  \mbox{\ttfamily
    CMUL}&\equiv&\frac{\nu_\mathrm{D}}{v}=\frac{3\sqrt{\pi}}{4}\left(\mathrm{erf}(1)-\mathrm{Ch}(1)\right)
  \frac{B_0}{G+\iota I}\mbox{\ttfamily nuPrime},\\
  \mbox{\ttfamily EFIELD}&\equiv&-\left[\frac{d\Phi}{dr}\right]_\mathrm{DKES}\frac{1}{vB_0}=-\frac{\iota}{G}\left[\frac{d\Psi}{dr}\right]_\mathrm{DKES}\mbox{\ttfamily EStar},
\end{eqnarray}
where $\mathrm{Ch}$ is the Chandrasekhar function and $\nu_\mathrm{D}$
is the actual pitch-angle deflection frequency of the particle.
\todo{These expressions are in SI units. Should there be some
  factors of $c$ to adhere to the Gaussian standard used here?
  Probably not.}
